Setting parameters for biological models with ANIMO

### 2014-02-03 Paper.tex
Wrong reference corrected (missed 'fig:')

By changing the title of a simulation, a user can keep track of different versions of their model,
which can be also kept and saved with the model, to be used in future sessions or for sharing purposes.
Should a user want to backtrack to a particular version of the network, the ``Reset to here'' button
can be used (see Fig.~\ref{animo-ui}, buttons above the graph). As an additional help to recall what a model version consisted of, the tooltip of
the ``Reset to here'' button shows an image of the network topology, taken in the moment when
the selected simulation was begun. A click on the ``Reset to here'' button will reset the
network topology and parameters at the ones used to generate the selected simulation.
As the adaptation of a model may proceed on different paths, the ``Difference with\dots'' and
``Reset to here'' buttons provide the user with some help with tracking the changes to the model
and selecting the most promising ones.

>>>>

By changing the title of a simulation, a user can keep track of different versions of their model,
which can be also kept and saved with the model, to be used in future sessions or for sharing purposes.
Should a user want to backtrack to a particular version of the network, the ``Reset to here'' button
can be used (see Fig.~\ref{fig:animo-ui}, buttons above the graph). As an additional help to recall what a model version consisted of, the tooltip of
the ``Reset to here'' button shows an image of the network topology, taken in the moment when
the selected simulation was begun. A click on the ``Reset to here'' button will reset the
network topology and parameters at the ones used to generate the selected simulation.
As the adaptation of a model may proceed on different paths, the ``Difference with\dots'' and
``Reset to here'' buttons provide the user with some help with tracking the changes to the model
and selecting the most promising ones.
